%% Start Paper
\documentclass[English, runningheads,a4paper]{llncs}
%
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{booktabs} 
\usepackage{multirow}
%\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{url}
%%% Autors %%%
\urldef{\mailsa}\path|mbakiri@cdta.dz,|
\urldef{\mailsb}\path|Christophe.Guyeux@femto-st.fr|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}


\begin{document}
\mainmatter  % start of an individual contribution

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Start Define the Title
% 1.0
\title{Survey on Hardware Implementation of Random Number Generators on FPGA: Theories and Experiments Analysis}

% 1.2
% a short form should be given in case it is too long for the running head
\titlerunning{Survey on Hardware Implementation of Random Number Generators}

% the name(s) of the author(s) follow(s) next
% 1.3
\author{Mohammed Bakiri\inst{1} \and Christophe Guyeux\inst{2}}

% (feature abused for this document to repeat the title also on left hand pages)
% 1.4 
%\authorrunning{Mohammed Bakiri\and Christophe Guyeux\ss er}

% the affiliations are given next
%1.5
\institute{Center for Development of Advanced Technologies, Baba Hassan, Alger, Algeria\and
FEMTO-ST Institute, UMR CNRS 6174, University of Franche-Comte, 25000, France.\\
\mailsa
\mailsb}

% 1.6 Creer le Titre
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
this paper introduce a survey on PRNG on FPGA.\dots

\keywords{Random Number Generator, PRNG, TRNG, Chaotic PRNG, Cryptography, Security, FPGA}
\end{abstract}

\section{Introduction}
\input{1-Introduction.tex}

\section{Terminologies and Basic Recall}
\input{2-Terminologies_and_Basic_Recall.tex}

\section{Random Number Generator: Theories and Classification}
We can find many implementation of RNG in Software and Hardware but all can be classifies generally as PRNG, TRNG and  Hybrid,  but new concept has been introduce this last year's defined by parallel and chaotic generator.

%%% All Type of PRNG
\subsection{PRNG}
\input{PRNG/PRNG.tex}

%%% All Type of TRNG
\subsection{TRNG}
\input{Others/TRNG.tex}

%%% All Type of Chaotic
\subsection{Chaotic Rundom Number Generator}
\input{Chaotic/Chaotic.tex}

%%% Compare ALL RNG for Statistic Test
\section{Rundom Number Generator:Statistic Test }
\input{4-Statistic_Test.tex}

%%% Compare ALL RNG for Statistic Test
\section{Rundom Number Generator: Cryptography Secure}
\input{5-Cryptography_Secure.tex}

%%% Compare ALL RNG for Statistic Test
\section{Rundom Number Generator: Hardware Implementation}
\input{6-Hardware_Implementation.tex}

%%% Conclusion
\section{Conclusion}
\input{7-Conclusion.tex}

\section{Reference}
\begin{thebibliography}{4}

%%%% CHAOS
\bibitem{lncschap} [CH-1] Pawel Dabal, Ryszard Pelka. : A Chaos-Based Pseudo-Random Bit Generator Implemented in FPGA Device. In: (2011)
\bibitem{lncschap}[CH-2] Pawel Dabal et all.:FPGA Implementation of Chaotic Pseudo-Random Bit Generators. In: (2012)
\bibitem{lncschap}[CH-3] Pawel Dabal, Ryszard Pelka. :A Study on Fast Pipelined Pseudo-Random Number Generator Based on Chaotic Logistic Map. In: 2014)  
\bibitem{lncschap}[CH-4] Lahcene Merah et all, :Coupling Two Chaotic Systems in Order to Increasing the Security of a Communication System - Study and Real Time FPGA Implementation. In (2013) 
\bibitem{lncschap}[CH-5] Hariprasad  NagaDeepa. Ch. :FPGA Implementation of A Cryptography Technology Using Pseudo Random Number Generator. In: (2013)   
\bibitem{lncschap}[CH-6] Ziqi Zhu and Hanping Hu. :A Dynamic Nonlinear Transform Arithmetic for Improving the Properties Chaos-based PRNG*. In (2010) 
\bibitem{lncschap}[CH-7] Yaobin Mao et all. :Design and FPGA Implementation of a Pseudo-Random Bit  Sequence Generator Using Spatiotemporal Chaos. In: (2009)
\bibitem{lncschap}[CH-8] Abhinav S. Mansingka. :Fibonacci-based Hardware Post-Processing for Non-Autonomous Signum Hyperchaotic System. In: (2013)
%%%% TRNG
\bibitem{lncschap}Viktor Fischer and Milos Drutarovsky. [TR-1]  (2002)
\bibitem{lncschap}Martin Simka et al,.:In: (2006) [TR-2] 
\bibitem{lncschap}Martin Simka et al,.:In: (2010) [TR-3]  
\bibitem{lncschap}Martin Simka et al,.:In: (2011) [TR-4] 
\bibitem{lncschap}Michal Varchola et al,.:In: (2008) [TR-5] 
\bibitem{lncschap}Paul Kohlbrenner et Kris Gaj .:In  (2004) [TR-6] 
\bibitem{lncschap}Cristian Klein et al.:In: (2009) [TR-7] ,
\bibitem{lncschap}K.H.Tsoi et al,.:In: (2003) [TR-8] 
\bibitem{lncschap}Markus Dichtl et Jovan Dj.Golic,.:In: (2007) [TR-9] 
\bibitem{lncschap}Abdelkarim Cherkaoui et al,.:In: (2013) [TR-10]
\bibitem{lncschap}Abdelkarim Cherkaoui et al,.:In: (2011) [TR-11]
\bibitem{lncschap}Abdelkarim Cherkaoui et al,.:In: (2013) [TR-12] 
\bibitem{lncschap}Ihor Vasyltsov et al.:In: (2008) [TR-13] 
\bibitem{lncschap}Mehrdad Majzoobi et al.:In: (2011) [TR-14] 
\bibitem{lncschap}Donggeon Lee,.In: (2014) [TR-15]
%%%% CA
\bibitem{lncschap}Tkacik.:In: (2003) [CA-1] 
\bibitem{lncschap}Juan C.Cerda and al.:in: (2012) [CA-2] 
\bibitem{lncschap}Juan C.Cerda and al.:.In: (2012) [CA-3] 
\bibitem{lncschap}Guan et al.:.In: (2004) [CA-4] 
\bibitem{lncschap}Leonidas Kotoulas et al,:.In: (2006) [CA-5] 
\bibitem{lncschap}Petre Anghelescu et al,:.In: (2007) [CA-6] 
\bibitem{lncschap}Ioana Dogaru and Radu Dogaru,:.In: (2010) [CA-7] 
\bibitem{lncschap}Lakshman Raut and David H. K. Hoe,:.In: (2013) [CA-8] 
\bibitem{lncschap}Dogaru Ioana and Dogaru Radu. :. In: (2014) [CA-9] 
  
\end{thebibliography}

\end{document}